\chapter{Introduction}
\label{c:intro}

% Background, Motivation and Relevant work
Multimodal problems that contain more than one region or more than one local optimum are common in the real world.
{\em Rastrigin function}, a hierachical problem which is composed of a larger unimodal and multiple smaller unimodals are also well-known in real-valued optimization.
In order to tackle these multimodal problems with a limited amount of resources, 
one needs to decide how much to invest for searching a better unimodal, 
while still maintain enough of exploitation on each potential unimodal.

The difficult part is that searching for a new unimodal and exploiting the best unimodal often require opposite searching behaviors.
For a fixed number of total evaluations, spending more time searching on one unimodal implies 
less attention on exploring other possible unimodals in the search space.
This is the common dilemma between {\em exploration} and {\em exploitation} for real-valued optimization algorithms.
Also, during different phases of optimization, 
the ratio between exploring new unimodals and exploiting the current best unimodal should be altered.
Exploration is more important in the beginning, while exploitation is more required in the end.
What makes this problem even harder is that in order to decrease the number of total evaluations, 
the size of the population are often limited in the real-valued optimization algorithms.
This means that as the number of unimodals to invest increases, the number of particles on each unimodal decreases.
This weakens the exploitation ability on each unimodal, making it less likely to identify new potential regions on each unimodal.

We are more interested in hierarchically decomposable problems.
With a certain amount of hints, we should be able to focus on one of the many potential unimodals, 
and identify when to invest more on certain unimodals to iteratively discover more smaller unimodals.
Also, we would like to only focus on some regions instead of the whole search spaces, in order to gain performance.
This requires detection of promising areas, and search space splitting techniques.
Moreover, after identifying certain interesting regions, we also need to decide how to allocate our resources.
Given the abilities described above, 
we can pay more attention on the promising regions and 
iteratively break down a difficult multimodal problem into smaller and easier unimodal problems.

% Thesis Objective
\section{Thesis Objectives}
This thesis proposes some techniques to break down multimodal problems into several unimodal problems in smaller non-overlapping subspaces.
It is under the consumption that solving one unimodal problem on a smaller subspace is easier than tackling the complete search space as a whole.
The techniques allow \textbf{identifing potential unimodals},
\textbf{defining a region of interest} to exploit, 
and \textbf{allocating resources} according to remaining evaluations.

Identifying a \textit{unimodal} depends on the sampling frequency and the underlying model.
Clustering is a common way for discovering potential unimodals.
The hierarchical clustering technique is used to discover unimodals in the fitness landscape.
The weighted normal distribution is adopted as the underlying consumption for unimodal, and reject overfitting models with minimum description length.

After identifying the unimodals by clustering, the search space is split into different regions of interest with linear projection.
Different projection matrices are assigned to project the original search space onto several subspaces with well-defined boundaries.
The projection matrices are also optimized so that each region would have minimum overlapping with others.
Searching in the smaller subspace enhances the probability of finding the optimum.
The well-defined boundaries are also needed for some algorithms.
The projection might also rotate or shear the original search space, making some inseparable problems easier to solve.

With multiple subspace to search, a new Multi-armed Bandit (MAB) technique is proposed
that optimize the resource allocation to get the greatest probability of obtaining a particle with the best rank.
Multi-armed bandit algorithms are suitable for this scenario, 
since it learns models from outcomes while the actions do not change the state of the world.
When there are still plenty of evaluations left, we should prefer exploration over exploitation and search equally on all subspaces.
However, when few evaluations remain, we should focus on the current best unimodal 
and try to exploit it to get the best fitness with the remaining evaluations.  


\section{Roadmap}
This thesis is composed of eight chapters.

\textbf{Chapter~\ref{chapter:algos}} presents three optimization algorithms that are used for comparisons.
We introduce 
the Covariance Matrix Adaptation Evolutionary Strategy (CMA-ES),
the Standard Particle Swarm Optimization (SPSO), and
the Ant Colony Optimization for Continous Domain (ACO$_R$).
These three algorithms each have different characteristics due to different underlying models.
We get a glimpse of how some common real-valued algorithms tackle multimodal problems. 


\textbf{Chapter~\ref{chapter:clustering}} first discusses our experience on using K-Means to identify unimodals.
Later, a more successful attempt of using the hierarchical clustering is presented.
Finally, we give details about Minimal Description Length and how it reduces number of clusters.

\textbf{Chapter~\ref{chapter:projection}} illustrates four basic affine transformation: translation, rotation, scaling and shearing.
Then the projective transformation and homogeneous coordinate are presented.
Finally, we give details about how we optimize our projection matrix in order to obtain ROIs with minimal-overlapping.


\textbf{Chapter~\ref{chapter:MAB}} first describes the Multi-armed Bandit Algorithm, 
A brief introduction of some common MAB algorithms are also given.
Then we present our new bandit techniques, that focus on acquiring the best rank in the cluster.


\textbf{Chapter~\ref{chapter:new_bandit}} gives details of our new technique.
It first describes the framework of the new technique.
Then a detailed process of initialization and unimodal detection is given.
The implementation detail of how to optimize the ROI and how to initialize arms are given.
Later, we discuss about how to decide which arm to pull in order to match the time-variant remain resource allocation.

\textbf{Chapter~\ref{chapter:experiments}} introduces the CEC 2005 benchmark problems that we used for experiment.
Then we give details about the experiment setup for different algorithms and the termination criteria.
The results are shown in figures that indicates the error after the same amount of evaluations.

\textbf{Chapter~\ref{chapter:conclusion}} summarizes this thesis. 
The conclusion and contributions are also given.
Some further improvements and future works are also discussed at the end.


